

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Dinh Vinh Khuong} \\ \vspace{1pt}
    \small 0352-917-477 $|$ \underline{\href{mailto:khuongdinhvinh@gmail.com}{khuongdinhvinh@gmail.com}}
    $|$ 
    \underline{\href{https://linkedin.com/in/dinhvinhkhuong}{linkedin.com/in/dinhvinhkhuong}}
   $|$
    \underline{\href{https://github.com/skylie628}{github.com/skylie628}}
\end{center}

%-----------OBJECTIVE-----------
\section{\textbf{Objective}}
  Software engineer passionate about web development. Proficient in frontend with experience in back-end development, dedicated to creating seamless user experiences and contributing to agile, scalable web solutions. 


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ho Chi Minh City University of Technology}{Thu Duc, HCM}
      {Bachelor of Engineering, Computer Science}{Nov 2022}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.15in, label={}]
  \resumeItemListStart
     \resumeItem{\textbf{Web technologies} : Javascript, Typescript, HTML5, CSS3}
     \resumeItem{ \textbf{Libraries & Frameworks}: React, Next, Redux, Jotai, Zustand, React-Query} 
    \resumeItem{   \textbf{UI Components}: Material UI, Ant Design, Chakra, Radix }
      \resumeItem{\textbf{Backend}: Familiar with Nodejs, Express, Mongo, Redis, SQL, Firebase}
      \resumeItem{\textbf{Tools}: Git, Docker, Webpack}
     \resumeItemListEnd
 \end{itemize}

%-----------EXPERIENCE-----------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Frontend Developer}{Jan 2023 -- Feb 2024}
      {Digimax}{ReactJS, Redux}
      \resumeItemListStart
        \resumeItem{Used ReactJS to create new features for users.}
       \resumeItem{Constructed front-end libraries and reusable parts for later use.}
        \resumeItem{Worked closely with UI designers to implement features, improve UI and UX from user
feedback.}
        \resumeItem{Analyzed requirements with Technical Architecture about new features. Select suitable
libraries and technologies, plan tasks and submit reports.}
        \resumeItem{Restructured the main app's structure, improve the maintainability of the code, keep the main.js file in the scratch React project at 400 kb, and shorten users' first load times.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Fullstack Intern }{Jul. 2021 -- Dec. 2021}
      {FPT Software} {HTML, CSS, Java Spring Boot }

      
      \resumeItemListStart
        \resumeItem{Utilized CSS library like Bootstrap, UI component and acquired knowledge of responsive design principles to create mobile-friendly layouts.}
       \resumeItem{Gained practical experience in web development using HTML, CSS, and JavaScript.}
        \resumeItem{Receive requirements from BA, plan tasks due, develop features, fix bugs and report
daily}
      
    \resumeItemListEnd

%-----------PROJECTS-----------
\section{\textbf{Projects}}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Crypto Portfolio Tracking} $|$ \emph{ReactJS, Redux, ChakraUI, HighCharts}}{Nov 2023 - Present} 
          
          \resumeItemListStart
          
            \resumeItem{Ultilized High Chart library to create interactive data visualization.}
            \resumeItem{Handled real-time data fetching with socket and Redux event listener}
            \resumeItem{Designed and implemented a cache system with Redis and AWS for data pooling.}
            \resumeItem{Integrated JWT-based authentication to ensure secure user access}
            \resumeItem{Demo: \underline{\href{https://coiport.vercel.app/}{coiport.vercel.app}} 
            }
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Ecommerce Site} $|$ \emph{Next - Typescript, Jotai, MongoDB, Redis}}{ Sep -- Dec 2023}
        
          \resumeItemListStart
          
            \resumeItem{
            Delivered a streamlined shopping experience, optimized performance, SEO and user satisfaction.}
            \resumeItem{Integrated Redis as a cache layer, enhancing product querying efficiency with MongoDB for agile product data storage.}
            \resumeItem{
             Applied Jotai as an atomic approach to global React state management
             }
               \resumeItem{Demo: \underline{\href{https://sadida-phonecase.vercel.app/}{sadida-phonecase.vercel.app}} 
            }
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{\textbf{Certifications}}
   \begin{itemize}[leftmargin=0.15in, label={}]
  \resumeItemListStart
  \resumeItem{Agile and Scrum Certification by Axon Active}
\resumeItem{TOEIC Certificate with score 725}
   \resumeItemListEnd
 \end{itemize}
%-------------------------------------------
\end{document}
